---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(repos = 'http://cran.us.r-project.org')
```

# gap 

## *(**`g`** olem **`a`** pp- **`p`** ackage)*

<!-- badges: start -->

[![Codecov test coverage](https://codecov.io/gh/mjfrigaard/gap/branch/main/graph/badge.svg)](https://app.codecov.io/gh/mjfrigaard/gap?branch=main)

<!-- badges: end -->

The goal of `gap` is to demonstrate the `golem` framework.

## Installation

You can install the development version of `gap` from [GitHub](https://github.com/) with:

```{r inst_pkg, eval=TRUE, message=FALSE, warning=FALSE}
install.packages("devtools")
devtools::install_github("mjfrigaard/gap")
```


## Run 

You can run the application with the following: 

```{r example, eval=FALSE}
library(gap)
gap::run_app()
```

## Code of Conduct

Please note that the `gap` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
