---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Shiny App-Packages (`sap`)

Shiny App-Packages, or `sap`, provides the code examples in for the [Shiny App-Packages](https://mjfrigaard.github.io/shiny-app-pkgs/) book and the [Developing & Testing Your Shiny Application](https://mjfrigaard.github.io/dev-test-shiny/) workshop provided at R in Pharma (2023).

Install `sap` using `remotes`:

```{r, eval=FALSE}
install.packages('remotes')
remotes::install_github('mjfrigaard/sap', ref = '22_pkgdown')
```

[`22_pkgdown`](https://github.com/mjfrigaard/sap/tree/22_pkgdown) demonstrates how to create a package website using `pkgdown` and GitHub Actions.

## Movie review data application

The original code and data for the Shiny app comes from the [Building Web Applications with Shiny](https://rstudio-education.github.io/shiny-course/) course.

Launch the application using; 

```{r, eval=FALSE}
library(sap)
launch_app()
```

