---
title: "Modules"
format: 
  html:
    toc: true
knitr:
  opts_chunk: 
    collapse: true
    comment: "" 

execute:
  echo: true

vignette: >
  %\VignetteIndexEntry{Modules}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup
#| include: false
library(lobstr)
```

## Application modules 

This vignette explains the movie review application's modules in the [`28_chores`](https://github.com/mjfrigaard/sap/tree/28_chores) branch of the `sap` package.

## Module files 

The module files in the R folder are listed below.

```{r}
#| eval: false
#| echo: false
#| collapse: true
fs::dir_tree("R", regexp = "mod")
```

```{verbatim}
├── mod_awards_point.R
├── mod_awards_tbl.R
├── mod_awards_vars.R
├── mod_compare_point.R
├── mod_compare_vars.R
├── mod_counts_bar.R
├── mod_counts_tbl.R
├── mod_counts_vars.R
├── mod_counts_vbox.R
├── mod_counts_waffle.R
├── mod_dist_box.R
├── mod_dist_raincloud.R
├── mod_dist_tbl.R
└── mod_dist_vars.R
```

## Module structure

The modules are structured into `compare`, `counts`, distribution (`dist`), and `awards`. The modules in the application have the following naming convention:

**`mod_` `<tab>` `_` `<type>` `_` `ui/server`**

-   `<tab>` is the name of the tab (**Compare**, **Counts**, **Distributions**, **Awards**)
-   **`<type>`**
    -   `vars`: 'variable' collection modules to return inputs    
    -   `tbl`: table display modules            
    -   type of display in module (i.e., `point`, `bar`, `vbox`, etc.)     

Each tab's modules are organized into abstract syntax trees[^ast] in the sections below. 

[^ast]: Create abstract syntax trees with the [`lobstr::ast()` function](https://lobstr.r-lib.org/reference/ast.html). 

### Compare 

```{verbatim}
█─launch_app 
├─█─display_type 
├─█─nav_ui 
│ ├─█─mod_compare_vars_ui 
│ └─█─mod_compare_point_ui 
└─█─nav_server 
  ├─█─mod_compare_vars_server 
  └─█─mod_compare_point_server
```

```{r}
#| echo: false
#| eval: false
lobstr::ast(
  launch_app(
    display_type(),
    nav_ui(
      mod_compare_vars_ui(),
      mod_compare_point_ui()
    ),
    nav_server(
      mod_compare_vars_server(),
      mod_compare_point_server()
    )
  )
)
```

### Counts 

```{verbatim}
█─launch_app 
├─█─display_type 
├─█─nav_ui 
│ ├─█─mod_counts_vars_ui 
│ ├─█─mod_counts_vbox_ui 
│ ├─█─mod_counts_bar_ui 
│ ├─█─mod_counts_waffle_ui 
│ └─█─mod_counts_tbl_ui 
└─█─nav_server 
  ├─█─mod_compare_vars_server 
  ├─█─mod_compare_point_server 
  ├─█─mod_counts_vars_sever 
  ├─█─mod_counts_vbox_server 
  ├─█─mod_counts_bar_server 
  ├─█─mod_counts_waffle_server 
  └─█─mod_counts_tbl_server 
```

```{r}
#| echo: false
#| eval: false
lobstr::ast(
  launch_app(
    display_type(),
    nav_ui(
      mod_counts_vars_ui(),
      mod_counts_vbox_ui(),
      mod_counts_bar_ui(),
      mod_counts_waffle_ui(),
      mod_counts_tbl_ui()
    ),
    nav_server(
      mod_compare_vars_server(),
      mod_compare_point_server(),
      mod_counts_vars_sever(),
      mod_counts_vbox_server(),
      mod_counts_bar_server(),
      mod_counts_waffle_server(),
      mod_counts_tbl_server()
    )
  )
)
```



### Distributions

```{verbatim}
█─launch_app 
├─█─display_type 
├─█─nav_ui 
│ ├─█─mod_dist_vars_ui 
│ ├─█─mod_dist_box_ui 
│ ├─█─mod_dist_raincloud_ui 
│ └─█─mod_dist_tbl_ui 
└─█─nav_server 
  ├─█─mod_dist_vars_server 
  ├─█─mod_dist_box_server 
  ├─█─mod_dist_raincloud_server 
  └─█─mod_dist_tbl_server 
    └─█─dist_var_summary 
```

```{r}
#| echo: false
#| eval: false
lobstr::ast(
  launch_app(
    display_type(),
    nav_ui(
      mod_dist_vars_ui(),
      mod_dist_box_ui(),
      mod_dist_raincloud_ui(),
      mod_dist_tbl_ui()
    ),
    nav_server(
      mod_dist_vars_server(),
      mod_dist_box_server(),
      mod_dist_raincloud_server(),
      mod_dist_tbl_server(
        dist_var_summary()
      )
    )
  )
)
```

### Awards 

```{verbatim}
█─launch_app 
├─█─display_type 
├─█─nav_ui 
│ ├─█─mod_awards_vars_ui 
│ ├─█─mod_awards_point_ui 
│ └─█─mod_awards_tbl_ui 
└─█─nav_server 
  ├─█─mod_awards_vars_server 
  ├─█─mod_awards_point_server 
  │ └─█─create_movie_awards 
  └─█─mod_awards_tbl_server
```

```{r}
#| echo: false
#| eval: false
lobstr::ast(
  launch_app(
    display_type(),
    nav_ui(
      mod_awards_vars_ui(),
      mod_awards_point_ui(),
      mod_awards_tbl_ui()
    ),
    nav_server(
      mod_awards_vars_server(),
      mod_awards_point_server(
        create_movie_awards()
      ),
      mod_awards_tbl_server()
    )
  )
)
```

## Launch 


```{verbatim}
█─launch_app 
├─█─display_type 
├─█─nav_ui 
│ ├─█─mod_compare_vars_ui 
│ ├─█─mod_compare_point_ui 
│ ├─█─mod_counts_vars_ui 
│ ├─█─mod_counts_vbox_ui 
│ ├─█─mod_counts_bar_ui 
│ ├─█─mod_counts_waffle_ui 
│ ├─█─mod_counts_tbl_ui 
│ ├─█─mod_dist_vars_ui 
│ ├─█─mod_dist_box_ui 
│ ├─█─mod_dist_raincloud_ui 
│ ├─█─mod_dist_tbl_ui 
│ ├─█─mod_awards_vars_ui 
│ ├─█─mod_awards_point_ui 
│ └─█─mod_awards_tbl_ui 
└─█─nav_server 
  ├─█─mod_compare_vars_server 
  ├─█─mod_compare_point_server 
  ├─█─mod_counts_vars_sever 
  ├─█─mod_counts_vbox_server 
  ├─█─mod_counts_bar_server 
  ├─█─mod_counts_waffle_server 
  ├─█─mod_counts_tbl_server 
  ├─█─mod_dist_vars_server 
  ├─█─mod_dist_box_server 
  ├─█─mod_dist_raincloud_server 
  ├─█─mod_dist_tbl_server 
  │ └─█─dist_var_summary 
  ├─█─mod_awards_vars_server 
  ├─█─mod_awards_point_server 
  │ └─█─create_movie_awards 
  └─█─mod_awards_tbl_server 
```

```{r}
#| echo: false
#| eval: false
lobstr::ast(
  launch_app(
    display_type(),
    nav_ui(
      mod_compare_vars_ui(),
      mod_compare_point_ui(),
      mod_counts_vars_ui(),
      mod_counts_vbox_ui(),
      mod_counts_bar_ui(),
      mod_counts_waffle_ui(),
      mod_counts_tbl_ui(),
      mod_dist_vars_ui(),
      mod_dist_box_ui(),
      mod_dist_raincloud_ui(),
      mod_dist_tbl_ui(),
      mod_awards_vars_ui(),
      mod_awards_point_ui(),
      mod_awards_tbl_ui()
    ),
    nav_server(
      mod_compare_vars_server(),
      mod_compare_point_server(),
      mod_counts_vars_sever(),
      mod_counts_vbox_server(),
      mod_counts_bar_server(),
      mod_counts_waffle_server(),
      mod_counts_tbl_server(),
      mod_dist_vars_server(),
      mod_dist_box_server(),
      mod_dist_raincloud_server(),
      mod_dist_tbl_server(
        dist_var_summary()
      ),
      mod_awards_vars_server(),
      mod_awards_point_server(
        create_movie_awards()
      ),
      mod_awards_tbl_server()

    )
  )
)
```
