---
title: "sap (Shiny App-Packages)"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{sap (Shiny App-Packages)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
	dev = "ragg_png",
	dpi = 320,
	out.width = "85%",
	fig.width = 6,
	fig.asp = 0.618,
	fig.retina = 2,
	fig.align = "center",
	fig.show = "hold"
)
```

```{r pkg, message=FALSE, warning=FALSE}
library(sap)
```

The `sap` package is designed to demonstrate how to build a Shiny application inside an R package. 

## Utility functions 

The utility functions in `sap` make it easier to wrangle data, write tests, render graphs, and display log messages/text logos.

### Tidy `ggplot2movies` data

```{r , echo=FALSE}
make_tidy_ggp2_movies <- function(movies_data_url) {
  movies_data <- read.csv(file = movies_data_url)
  # specify genre columns
  genre_cols <- c(
    "Action", "Animation",
    "Comedy", "Drama",
    "Documentary", "Romance",
    "Short"
  )
  # calculate row sum for genres
  movies_data$genre_count <- rowSums(movies_data[, genre_cols])
  # create aggregate 'genres' for multiple categories
  movies_data$genres <- apply(
    X = movies_data[, genre_cols],
    MARGIN = 1,
    FUN = function(row) {
      genres <- names(row[row == 1])
      if (length(genres) > 0) {
        return(paste(genres, collapse = ", "))
      } else {
        return(NA)
      }
    }
  )
  # format variables
  movies_data$genre_count <- as.integer(movies_data$genre_count)
  movies_data$genre <- ifelse(test = movies_data$genre_count > 1,
    yes = "Multiple genres",
    no = movies_data$genres
  )
  movies_data$genre <- as.factor(movies_data$genre)
  movies_data$mpaa <- factor(movies_data$mpaa,
    levels = c("G", "PG", "PG-13", "R", "NC-17"),
    labels = c("G", "PG", "PG-13", "R", "NC-17")
  )

  # reduce columns to only those in graph
  movies_data[, c(
    "title", "year", "length", "budget",
    "rating", "votes", "mpaa", "genre_count",
    "genres", "genre"
  )]
}
```

The `make_tidy_ggp2_movies()` function was written to wrangle the `ggplot2movies` data into a 'tidy' format.

```{r}
ggp2mov_url <- "https://raw.githubusercontent.com/hadley/ggplot2movies/refs/heads/master/data-raw/movies.csv"
```

```{r make_tidy_ggp2_movies}
tidy_movies <- make_tidy_ggp2_movies(movies_data_url = ggp2mov_url)
str(tidy_movies)
```

This function is not exported from the package, it lives in `tests/testthat/fixtures/make-tidy_ggp2_movies.R`.

### Test helpers

```{r echo=FALSE}
make_ggp2_inputs <- function() {
  glue::glue_collapse("list(x = 'rating',
     y = 'length',
     z = 'mpaa',
     alpha = 0.75,
     size = 3,
     plot_title = 'Enter plot title'
     )")
}
make_var_inputs <- function() {
  glue::glue_collapse("list(y = 'audience_score',
     x = 'imdb_rating',
     z = 'mpaa_rating',
     alpha = 0.5,
     size = 2,
     plot_title = 'Enter plot title'
    )")
}
```

The `make_var_inputs()` and `make_ggp2_inputs()` functions make it easier to create test inputs for modules:

```{r make_var_inputs, collapse=FALSE, comment=""}
make_var_inputs()
```

```{r make_ggp2_inputs, collapse=FALSE, comment=""}
make_ggp2_inputs()
```

These live in `tests/testthat/helper.R` and are not exported from the package.

### Create scatter plot

The `scatter_plot()` function was written to make it easier to use `ggplot2` functions in the `mod_scatter_display_server()` function. 

Variable inputs are collected from the UI as strings (i.e., `"length"` and `"rating"`, not `length` and `rating`), which makes it difficult for standard `ggplot2` calls: 

```{r}
ggplot2::ggplot(data = na.omit(tidy_movies), 
  mapping = ggplot2::aes(
    x = length,
    y = rating, 
    color = mpaa)) + 
  ggplot2::geom_point(
    alpha = 0.75,
    size = 2)
```

`scatter_plot()` allows for strings to be passed to the rendering functions:

```{r}
scatter_plot(
  df = na.omit(tidy_movies),
  x_var = "length",
  y_var = "rating",
  col_var = "mpaa",
  alpha_var = 0.75,
  size_var = 2
)
```

### Logs and logos

`log_message()` uses base R functions and is simple but effective. 

```{r}
log_message(
  message = "A log message", 
  save = FALSE)
```

`logr_msg()` is written with the `logger` package and has additional arguments: 

```{r}
logr_msg(
  message = "A log message", 
  level = "INFO", 
  store_log = FALSE)
#> INFO [2025-03-05 13:57:53] A log message
```

## Applications

### Default (`movies`)

```{r echo=FALSE, comment=""}
fs::dir_tree("../inst/www")
```

```{r eval=FALSE}
launch_app()
```

### bslib (`movies`)

```{r echo=FALSE, comment=""}
fs::dir_tree("../inst/www")
```


```{r eval=FALSE}
launch_app(app = 'bslib')
```

### ggp2 (tidy `ggplot2movies`)

```{r echo=FALSE, comment=""}
fs::dir_tree("../inst/tidy-movies")
```


```{r eval=FALSE}
launch_app(app = 'ggp2')
```

### quarto 

```{r echo=FALSE, comment=""}
fs::dir_tree("../inst/quarto")
```

```{r eval=FALSE}
launch_app(app = 'quarto')
```

