---
title: "test-specs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{test-specs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shinyAppPkgs)
```

## Movies App Specifications

**Example:** The application should source movie review data from platforms like IMDB or Rotten Tomatoes

### Feature

**Feature:** Movie Review Dataset Variables

***As a*** user

***I want to*** have a dataset with variables from IMDB and Rotten Tomatoes

***In order to*** provide comprehensive movie reviews

### **Background**:

***Given*** the application has access to data from the IMDB and Rotten Tomatoes APIs

## Functional Requirements (**Scenarios**)

**Scenario**: Movie Review Continuous and Categorical Variables

***When*** the application loads from IMDB and Rotten Tomatoes movie review data

***Then*** the dataset should include a continuous critic ratings variable

***And*** the dataset should include a continuous audience ratings variable

***And*** the dataset should include a categorical mpaa ratings variable

***And*** the dataset should include a categorical genres variable

## Traceability matrix

+-----------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------+----------------------------------------------------------------------------------+-------------+
| Specifications                                                                                      | Features                                                                    | Requirements                                                                     | Test        |
+=====================================================================================================+=============================================================================+==================================================================================+=============+
| **S1**: The application should source movie review data from platforms like IMDB or Rotten Tomatoes | **F1.1**:                                                                   | **Scenario**: Movie Review Continuous and Categorical Variables                  | ?           |
|                                                                                                     |                                                                             |                                                                                  |             |
|                                                                                                     | **Feature:** Movie Review Dataset Variables                                 | ***When*** the application loads from IMDB and Rotten Tomatoes movie review data |             |
|                                                                                                     |                                                                             |                                                                                  |             |
|                                                                                                     | ***As a*** user                                                             | ***Then*** the dataset should include a continuous critic ratings variable       |             |
|                                                                                                     |                                                                             |                                                                                  |             |
|                                                                                                     | ***I want to*** have a dataset with variables from IMDB and Rotten Tomatoes | ***And*** the dataset should include a continuous audience ratings variable      |             |
|                                                                                                     |                                                                             |                                                                                  |             |
|                                                                                                     | ***In order to*** provide comprehensive movie reviews                       | ***And*** the dataset should include a categorical mpaa ratings variable         |             |
|                                                                                                     |                                                                             |                                                                                  |             |
|                                                                                                     | **Background**:                                                             | ***And*** the dataset should include a categorical genres variable               |             |
|                                                                                                     |                                                                             |                                                                                  |             |
|                                                                                                     | ***Given*** the application has access to IMDB and Rotten Tomatoes APIs     |                                                                                  |             |
+-----------------------------------------------------------------------------------------------------+-----------------------------------------------------------------------------+----------------------------------------------------------------------------------+-------------+