---
title: "test-specs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{test-specs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(moviesApp)
```

# Scatter Plot Specifications

**US1**: Shiny App Scatter Plot Data Visualization for Movie Review Explorer:

-   The application should source movie review data from platforms like IMDB or Rotten Tomatoes and should encompass both continuous variables (e.g., audience and critic reviews) and categorical variables (e.g., MPAA ratings).

-   Users should have dropdown menus for selecting continuous variables for x and y axes, and a separate dropdown to choose a categorical variable (to color the points in the scatter plot).

-   The application should also have sliders or similar controls for users to adjust the size and opacity of the points (allowing them to handle overlapping points more effectively). Finally, users should have the option to enter text and provide a custom title for the scatter plot.

## Scatter Plot: Feature Requirement

**Movie review app Scatter plot data visualization features:**

**F1.1**: The movie review data should contain continuous variables (e.g., critic and audience ratings) and categorical variables (e.g., mpaa, genres) from IMDB and Rotten Tomatoes.

**F1.2**: The UI should display dropdown menus for selecting continuous variables on both the x-axis and y-axis, and a dropdown menu categorical variable for point coloration.

**F1.3**: Incorporate sliders or similar controls for adjusting point size and point opacity.

**F1.4**: Provide input field for users to enter an optional scatter plot title.

### Scatter Plot: Functional Requirements

-   **FR 1.1**: The app data should be from IMDB and Rotten Tomatoes containing both continuous and categorical variables stored in a tabular format.\n

-   **FR 1.2**: The app should display dropdown menus listing available continuous variables for x-axis and y-axis selection.

-   **FR 1.3**: Upon user selection of x-axis and y-axis variables, the app should update the scatter plot to reflect the user's choices.

-   **FR 1.4**: The app should present a dropdown menu listing available categorical variables for point coloration.

-   **FR 1.5**: The app should dynamically change the color of points in the scatter plot based on the user's categorical variable selection.

-   **FR 1.6**: The app should provide a slider control that allows users to adjust the size of the points, ranging from a pre-defined minimum to a maximum size.

-   **FR 1.7**: The app should offer an opacity control, letting users adjust the transparency of points from fully opaque to fully transparent.

-   **FR 1.8**: The app should display an input field where users can type in a custom title for the scatter plot.

-   **FR 1.9**: Upon user entry or modification in the title input field, the app should update the scatter plot's title in real-time.

### Traceability matrix

+------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+------+
| Specifications                                                               | Features                                                                                                       | Requirements                                                                                                                                                        | Test |
+==============================================================================+================================================================================================================+=====================================================================================================================================================================+======+
| **US1**: Shiny App Scatter Plot Data Visualization for Movie Review Explorer | **F1.1**: IMDB and Rotten Tomatoes data with continuous (i.e., scores) and categorical (i.e., mpaa) variables. | **FR 1.1**: The app should display movie review data from IMDB and Rotten Tomatoes containing both continuous and categorical variables stored in a tabular format. | ?    |
+------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+------+
|                                                                              | **F1.2**: Dropdown menus (continuous x & y axes, categorical point coloration)                                 | **FR 1.2**: The app should display dropdown menus listing available continuous variables for x-axis and y-axis selection.                                           | T2   |
+------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+------+
|                                                                              |                                                                                                                | **FR 1.3**: Upon user selection of x-axis and y-axis variables, the app should update the scatter plot to reflect the user's choices.                               | T3   |
+------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+------+
|                                                                              |                                                                                                                | **FR 1.4**: The app should present a dropdown menu listing available categorical variables for point coloration.                                                    | T2   |
+------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+------+
|                                                                              |                                                                                                                | **FR 1.5**: The app should dynamically change the color of points in the scatter plot based on the user's categorical variable selection.                           | T3   |
+------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+------+
|                                                                              | **F1.3**: Controls (point size & opacity)                                                                      | **FR 1.6**: The app should provide a slider control that allows users to adjust the size of the points, ranging from a pre-defined minimum to a maximum size.       | ?    |
|                                                                              |                                                                                                                |                                                                                                                                                                     |      |
|                                                                              |                                                                                                                | **FR 1.7**: The app should offer an opacity control, letting users adjust the transparency of points from fully opaque to fully transparent.                        |      |
+------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+------+
|                                                                              | **F1.4:** Input text field (optional title)                                                                    | **FR 1.8**: The app should display an input field where users can type in a custom title for the scatter plot.                                                      | ?    |
|                                                                              |                                                                                                                |                                                                                                                                                                     |      |
|                                                                              |                                                                                                                | **FR 1.9**: Upon user entry or modification in the title input field, the app should update the scatter plot's title in real-time.                                  |      |
+------------------------------------------------------------------------------+----------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------+------+
