---
title: "test-specs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{test-specs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tibble)
library(dplyr)
library(tidyr)
library(testthat)
```

```{r pkg}
library(moviesApp)
```

# Scatter Plot: User Requirement

**US1**: '*As an film analyst, I want to view an interactive scatter plot in a dashboard that consolidates movie reviews from multiple sources so that I can compare and analyze trends and outliers in movie ratings quickly.*'

## Scatter Plot: Feature Requirement

**FE1**: '*Given that movie reviews are available on multiple websites, when the user selects a rating metric from the application display, the interactive scatter plot should allow for comparisons from at least two data sources (i.e., IMDb, Rotten Tomatoes), and include options for selecting other variables of interest (i.e., audience scores, runtime, etc.).'*

### Scatter Plot: Functional Requirements

-   **FR1**: The system will display movie reviews from IMDb and Rotten Tomatoes collected from their respective APIs.

-   **FR2**: The scatter plot will be displayed on the dashboard and updated with new user inputs.

-   **FR3**: Each data point on the scatter plot will represent a movie and be color-coded based on the following categories: MPAA ratings, genre, title type, critics rating, and audience rating.

-   **FR4**: The scatter plot will have labeled axes, a legend to differentiate between data sources, and a customizable title.

### Traceability matrix

| User Specification                   | Feature Requirement                                                          | Functional Requirements        | Test    |
|--------------|:------------------------------|:-------------|--------------|
| UR1: scatter plot data visualization | FE1: interactive scatter plot (two data sources, drop-down variable options) | FR1: data source               | T1 & T2 |
|                                      |                                                                              | FR2: user-input updating       | T5 & T6 |
|                                      |                                                                              | FR3: color-coded data points   | T3      |
|                                      |                                                                              | FR4: plot axis, legend & title | T4      |

