---
title: "Movies Report"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
params:
  plot_obj: NA
  x_var: NA
  y_var: NA
  data: NA
  generated_on: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(DT)
library(knitr)
```

## Report Summary

This report was generated on `r format(params$generated_on, "%Y-%m-%d at %H:%M:%S")` and contains an analysis of the movies dataset.

## Visualization

The following scatter plot shows the relationship between `r params$x_var` and `r params$y_var`:

```{r plot, fig.width=10, fig.height=6}
print(params$plot_obj)
```

## Data Summary

### Dataset Overview

The filtered dataset contains **`r nrow(params$data)`** observations across **`r ncol(params$data)`** variables.

### Genre Distribution

```{r genre-summary}
genre_counts <- table(params$data$genre)
kable(data.frame(
  Genre = names(genre_counts),
  Count = as.numeric(genre_counts)
), caption = "Number of movies by genre")
```

### Statistical Summary

```{r summary-stats}
# Select numeric columns for summary
numeric_cols <- sapply(params$data, is.numeric)
if(any(numeric_cols)) {
  summary_data <- params$data[, numeric_cols, drop = FALSE]
  kable(do.call(cbind, lapply(summary_data, function(x) {
    c(Mean = round(mean(x, na.rm = TRUE), 2),
      Median = round(median(x, na.rm = TRUE), 2),
      SD = round(sd(x, na.rm = TRUE), 2),
      Min = round(min(x, na.rm = TRUE), 2),
      Max = round(max(x, na.rm = TRUE), 2))
  })), caption = "Summary statistics for numeric variables")
}
```

## Data Table

Below is the complete filtered dataset:

```{r data-table}
DT::datatable(
  params$data,
  options = list(
    pageLength = 15,
    scrollX = TRUE
  ),
  rownames = FALSE
)
```

## About the Data

The movies dataset contains information on 651 randomly sampled movies produced and released before 2016, sourced from Rotten Tomatoes and IMDB.

**Selected variables include:**

- Title, genre, MPAA rating, studio, runtime
- Theatrical and DVD release dates
- IMDB rating and number of votes
- Rotten Tomatoes critics score / rating and audience score / rating
- Oscar nomination and win indicators (best picture, actor, actress, director)
- Director and top-billed cast

---

*Report generated by the Movies Explorer Shiny Application*
